Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex
filled in some defs, etc

@@

\begin{definition}
  Embeds, embeddable

  \raf{I think we want to say $\Gamma$ embeds $\gamma$, and then a loss $L$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.}
\end{definition}

@@

\begin{theorem}
  Every finite elicitable property is embeddable.
\end{theorem}

\begin{definition}
  A property refines another
\end{definition}

@@

\begin{definition}
  $d$-embeddable, $\elicembed$
\end{definition}

@@

\raf{Cite the proof of the theorem saying every finite elicitable property is embeddable.}
\begin{corollary}
  Every finite elicitable property is $(n-1)$-embeddable.
\end{corollary}
\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}

>>>>

\begin{definition}
  A loss \emph{indirectly elicits} a property $\gamma$ if it elicits a property with a calibrated link to $\gamma$.
\end{definition}

@@

\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
  Finally, we say $\gamma$ is \emph{$d$-embeddable}, or just \emph{embeddable}, if such an $L$ exists and is convex.
\end{definition}

@@

\begin{theorem}
  Every finite elicitable property is $(n-1)$-embeddable.
\end{theorem}
\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}

\begin{definition}
  Let $\Gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$.
  Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.
  That is, the cells of $\Gamma'$ are all contained in cells of $\Gamma$.
\end{definition}

@@

\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ such that $\gamma$ is $d$-embeddable.
\end{definition}

@@
